Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-10-07 paper.tex
added bibliography

        Many neuroimaging workflow engines currently exist. Examples include
        Nipype, Pipeline System for Octave and Matlab (PSOM), LONI, SPM, FastR,
        Automatic Analysis (AA) and Pydpiper\note{add citations here}. These 
        workflow engines aim to satisfy four criteria: 1) straightforward \tristan{easy? facilitated?} 
        workflow composition, 2) performance, 3) portability of the workflows 
        and 4) reproducibility of the analyses. While these workflow engines
        do tackle performance, it is mainly limited to minimizing computation
        time and does not consider data transfer times -- which are typically
        costly in Big Data settings. Therefore, these engines need to be adapted
        for the processing of neuroimaging data.

@@

        Current studies show that different tools 
        performing the same function, in addition to the same versions of tools 
        executing on top of different operating systems, produce significantly 
        dissimilar results \cite{bowring, gronenschild 2011, glatard 2015}. As a result, it is necessary that specific details 
        on the workflow, such a data used, software versions and operating 
        system used are provided. For this reason, many workflow engines have
        incorporated provenance tracking into their design. \tristan{Provenance is also
        a way to merely document what happened so that results can be traced.}

@@

    \addcontentsline{toc}
        {chapter}{Bibliography} 
        \bibliography{bibliography}
        \bibliographystyle{ieeetr}
\end{document}

>>>>

        Many neuroimaging workflow engines currently exist. Examples include
        Nipype~\cite{nipype}, Pipeline System for Octave and Matlab (PSOM)~\cite{10.3389/fninf.2012.00007}, LONI~\cite{REX20031033}, SPM~\cite{spm}, FastR~\cite{10.3389/fict.2016.00015},
        Automatic Analysis (AA)~\cite{10.3389/fninf.2014.00090} and Pydpiper~\cite{10.3389/fninf.2014.00067}. These 
        workflow engines aim to satisfy four criteria: 1) straightforward \tristan{easy? facilitated?} 
        workflow composition, 2) performance, 3) portability of the workflows 
        and 4) reproducibility of the analyses. While these workflow engines
        do tackle performance, it is mainly limited to minimizing computation
        time and does not consider data transfer times -- which are typically
        costly in Big Data settings. Therefore, these engines need to be adapted
        for the processing of neuroimaging data.

@@

        Current studies show that different tools 
        performing the same function, in addition to the same versions of tools 
        executing on top of different operating systems, produce significantly 
        dissimilar results \cite{bowring, gronenschild2011, glatard2015}. As a result, it is necessary that specific details 
        on the workflow, such a data used, software versions and operating 
        system used are provided. For this reason, many workflow engines have
        incorporated provenance tracking into their design. \tristan{Provenance is also
        a way to merely document what happened so that results can be traced.}

@@

    \addcontentsline{toc}
        {chapter}{Bibliography} 
        \bibliographystyle{ieeetr}
        \bibliography{bibliography}
\end{document}
